The Effects of the NBA COVID Bubble on the NBA Playoffs: A Case Study for Home-Court Advantage

### 2022-01-26 Manuscript/manuscript.tex
Update manuscript.tex
Updated table with adjusted p-values(still need to decide whether or not to remove 1 of parametric or non-parametric p-values like reviewer 1 suggested)

\begin{table}
  \caption{The results from the 9 tests.}
  \label{tab:table}
\centering
\begin{tabular}[t]{lcccc}
  \toprule
  & 2020 & 2017-19 & \multicolumn{2}{c}{P-value}\\
  \cmidrule(lr){4-5}
  &          &                & Z-test & Wilcoxan\\
\midrule
Home Win & 0.482 & 0.613 & 0.0497 & 0.0400\\
Home Scoring & 1.101 & 1.081 & 0.2321 & 0.2985\\
Away Scoring & 1.091 & 1.040 & 0.0008 & 0.0004\\
Home 2P & 0.523 & 0.515 & 0.4335 & 0.5719\\
Home 3P & 0.363 & 0.357 & 0.5733 & 0.8852\\
Home FT & 0.793 & 0.774 & 0.0692 & 0.0496\\
Away 2P & 0.536 & 0.504 & 0.0003 & 0.0003\\
Away 3P & 0.357 & 0.346 & 0.3256 & 0.3081\\
Away FT & 0.783 & 0.777 & 0.6601 & 0.8370\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
  \caption{The results from the 9 tests.}
  \label{tab:table}
\centering
\begin{tabular}[t]{lcccccc}
  & 2020 & 2017-19 & \multicolumn{2}{c}{P-value} & \multicolumn{2}{c}{Adjusted P-value}\\
  &          &                & Z-test & Wilcoxan & Z-test & Wilcoxan\\
Home Win & 0.482 & 0.613 & 0.0497* & 0.0400* & .4473 & 0.3598\\
Home Scoring & 1.101 & 1.081 & 0.2321 & 0.2985 & 1 & 1\\
Away Scoring & 1.091 & 1.040 & 0.0008* & 0.0004* & 0.0075* & 0.0035*\\
Home 2P & 0.523 & 0.515 & 0.4335 & 0.5719 & 1 & 1\\
Home 3P & 0.363 & 0.357 & 0.5733 & 0.8852 & 1 & 1\\
Home FT & 0.793 & 0.774 & 0.0692 & 0.0496* & 0.6228 & 0.4464\\
Away 2P & 0.536 & 0.504 & 0.0003* & 0.0003* & 0.0030 & 0.0023\\
Away 3P & 0.357 & 0.346 & 0.3256 & 0.3081 & 1 & 1\\
Away FT & 0.783 & 0.777 & 0.6601 & 0.8370 & 1 & 1\\
\end{tabular}
\end{table}
